Value Ordering, Discrepancies, and Restarts for Subgraph Algorithms\thanks{This footnote leaves room for a piece of text saying how grateful we are to our funding agency. This includes a magic grant number, so it takes up three precious lines of space.}

### 2018-01-29 paper/paper.tex
660

Performance results from these two modified algorithms, using the same families of instances as in
the previous section, are shown in \cref{figure:kdown,figure:mcsplit,figure:mcs}. Although we have
moved from a decision problem to an optimisation problem, the same changes remain clearly
beneficial. For the $k{\downarrow}$ algorithm, the change has a minimal effect on many instances
(typically, where the $k = 0$ subproblem is unsatisfiable and hard, and the $k = 1$ subproblem is
satisfiable and easy), but gives large benefits on many more instances than it penalises: it is over
an order of magnitude better on nearly a hundred instances, whilst being an order of magnitude worse
on only five.

>>>>

Performance results from these two modified algorithms, using the same families of instances as in
the previous section, are shown in \cref{figure:kdown,figure:mcsplit,figure:mcs}. Although we have
moved from a decision problem to an optimisation problem, the same changes remain clearly
beneficial. For the $k{\downarrow}$ algorithm, the change has a minimal effect on many instances
(typically, where the $k = 0$ subproblem is unsatisfiable and hard, and the $k = 1$ subproblem is
satisfiable and easy), but gives large benefits on many more instances than it penalises: it is over
an order of magnitude better on nearly a hundred instances, whilst being an order of magnitude worse
on only seven.
